Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-18 paper-2023-acsos-pulverization.tex
explain the role of the state

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strength;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$ \meta{
    NICOLAS what does this do? write within this meta block.
    %
    Hold in memory the updated distances between the devices.
};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.

>>>>

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strength;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$, storing the distances measured by the device;
%\meta{
%    NICOLAS what does this do? write within this meta block.
%    %
%    Hold in memory the updated distances between the devices.
%};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.
